### 2015-06-11 ApresentacoesArtigos/quali/quali.tex
arrumacoes minimas

%  \usepackage{titlesec}
  \titleformat{\chapter}[display]
  {\normalfont\bfseries\filcenter}
  {\LARGE\thechapter}
  {1ex}
  {\titlerule[2pt]
	  \vspace{2ex}%
  \LARGE}
  [\vspace{1ex}%
  {\titlerule[2pt]}]

@@

{\noindent
	Complex networks form one of the most active fields of recent physics.
	With respectable efforts for exhibiting advances to the general audience, 
	it seems, however, that few or none of these are targeted to the individual profit.
	That is, with a core knowledge about the field, and recipes for harnessing,
	provide means for the participant to interact and understand the networks they are in.
	This work aims to accomplish such task by means of the social networks of the participants.
	We verified basic ubiquitous characteristics in such networks, such as time stability of topological measures,
	of basic connective sector sizes and the differentiation of the textual production.
	We also formalized conceptualizations of these networks as OWL were they were possible, specially
	in relation to the social participation instances provided by law. Finally, software and
	data have been put available and used, as means to enable integrated analysis of different provenance and public benefit.
	Conceptual consequences have been documented and requires anthropological considerations.
	Furthermore, software, ontological and data contributions can be better documented and developed while
	a typological consideration of the physical properties observed in human interaction networks should
	bridge complex networks and more the traditional legacy of human sciences on the subject.
}

>>>>

%  \usepackage{titlesec}
  \titleformat{\chapter}[display]
  {\normalfont\bfseries\filcenter}
  {\LARGE\thechapter}
  {-2ex}
  {%\titlerule[2pt]
	 % \vspace{2ex}%
  \LARGE}
  [%\vspace{1ex}%
  {\titlerule[1pt]}]

@@

{\noindent
	Complex networks form one of the most active fields of recent physics.
	With respectable efforts for exhibiting advances to the general audience, 
	it seems, however, that few or none of these are targeted to the benefit of the individual that constitute such systems.
	That is, with a core knowledge about the field, and recipes for harnessing,
	provide means for the participant to interact and understand the networks he/she is in.
	This work aims to accomplish such task by means of the social networks of the participants.
	We verified that such networks exhibit time stability of topological measures and
	of basic connective sector sizes and exhibit differentiation of the textual production in each basic connective sector.
	We also formalized conceptualizations of these networks as OWL were they were possible, specially
	in relation to the social participation instances provided by law. Finally, software and
	data have been put available and used, as means to enable integrated analysis of different provenance and public benefit.
	Conceptual consequences have been documented and requires anthropological considerations.
	Furthermore, software, ontological and data contributions can be better documented and developed while
	a typological consideration of the physical properties observed in human interaction networks should
	bridge complex networks and the more traditional legacy of human sciences on the subject.
}
